---
title: "Short Assignment 2"
description: |
 Short assignment 2 for Political and Social Network Analysis
author:
  - name: Dana Nestor
    url: https://dnestor.github.io/
    affiliation: UMASS DACSS
    affiliation_url: https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program
date: 02-02-2022
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(statnet)
library(igraph)
library(dplyr)
library(readr)
```

Utilizing the provided bill cosponsorship data from the 112th congress and (modified) related import scripts, I read-in a CSV file and built both igraph and statnet objects to commence investigation. This data contains unique identifiers for each Member, the bill number, the date the Member joined in cosponsorship (and left, if applicable) and whether or not the member was an original co-sponsor.

```{r}
data <- read_csv("~/DACSS/Network Analysis/govtrack_cosponsor_data_112_congress.csv")

# Provided script, modified so it would work with the available data
 nodes <- data[c("name","thomas_id","bioguide_id","state","district")]
  nodes <- distinct(nodes, name, state, bioguide_id, thomas_id, .keep_all = TRUE)
  
  #There are repeat entries for congress people who are given both a thomas_id (old system) and a
  #bioguide_id (new system). Lets fix this by splitting and merging. 
    nodes_a  <- nodes[is.na(nodes$thomas_id),]
    nodes_a  <- nodes[c("name","state","district","bioguide_id")]
    nodes_b  <- nodes[is.na(nodes$bioguide_id),]
    nodes_b  <- nodes[c("name","state","district","thomas_id")]
    nodes    <- merge(x = nodes_a, y = nodes_b, by = c("name","state","district"), all = TRUE)
    rm(nodes_a);rm(nodes_b)
  
  #Lets also create a new ID that will be assigned to all congress people
    nodes$ID <- 1:nrow(nodes)
  
  #Lets reorder the data putting the ID first
    nodes <- nodes[c("ID","name","state","district","bioguide_id","thomas_id")]
  
#Now let's create a dataframe that contains just edge atributes
  #Lets add the from_id collumn, replacing all the node attributes given for the senator cosponsoring
    edge_list <- data
    edge_list$node_1[!is.na(edge_list$thomas_id)]    <- nodes$ID[match(edge_list$thomas_id, nodes$thomas_id)][!is.na(edge_list$thomas_id)]
    edge_list$node_1[!is.na(edge_list$bioguide_id)]  <- nodes$ID[match(edge_list$bioguide_id, nodes$bioguide_id)][!is.na(edge_list$bioguide_id)]
    edge_list <- edge_list[c("node_1","bill_number","original_cosponsor","date_signed","date_withdrawn","sponsor")]
  
  #At this point, the "edges" dataframe contains links between sponsors and bills. Instead we want want 
  #the edgelist to represent to links between legislators. 
  #Let's do that by replacing the bill number collumn with the ID of the bill's original sponsor
    sponsor_key    <- edge_list[edge_list$sponsor == TRUE, c("node_1","bill_number")]
    edge_list$node_2   <- sponsor_key$node_1[match(edge_list$bill_number, sponsor_key$bill_number)]
    
  #Lets reorder the dataframe, putting the edgelist in the first two collumns
      edge_list <- edge_list[c('node_1', 'node_2', 'bill_number','sponsor', 'original_cosponsor', 'date_signed', 'date_withdrawn')]
    
  #We dont need to keep the looped connections that represent legislators sponsoring their own bills
      edge_list <- edge_list[edge_list$sponsor == FALSE,]
  
  #We can now remove the sponsor collum
      edge_list <- edge_list[c('node_1', 'node_2', 'bill_number','original_cosponsor', 'date_signed', 'date_withdrawn')]
      
  #And remove unessesary objects
      rm(sponsor_key)

#Now let's make an igraph object
  network_igraph <- graph_from_data_frame(d = edge_list, directed = TRUE, vertices = nodes)
  
#Now lets create a statnet object
  
  network_statnet <- network(as.matrix(edge_list[1:2]), matrix.type = "edgelist", directed = TRUE)
  
  network_statnet%e%'bill_number'         <- as.character(edge_list$bill_number)
  network_statnet%e%'original_cosponsor'  <- as.character(edge_list$original_cosponsor)
  network_statnet%e%'date_signed'         <- as.character(edge_list$date_signed)
  network_statnet%e%'date_withdrawn'      <- as.character(edge_list$date_withdrawn)
  
  network_statnet%v%'name'        <-as.character(nodes$name[match(nodes$ID,network_statnet%v%'vertex.names')])
  network_statnet%v%'state'       <-as.character(nodes$state[match(nodes$ID,network_statnet%v%'vertex.names')])
  network_statnet%v%'district'    <-as.character(nodes$district[match(nodes$ID,network_statnet%v%'vertex.names')])
  network_statnet%v%'bioguide_id' <-as.character(nodes$bioguide_id[match(nodes$ID,network_statnet%v%'vertex.names')])
  network_statnet%v%'thomas_id'   <-as.character(nodes$thomas_id[match(nodes$ID,network_statnet%v%'vertex.names')])
  

#Lets create properly named objects and delete unessesary ones
  network_nodes <- nodes
  network_edgelist <- edge_list
  rm(nodes);rm(data);rm(edge_list)
```

In further examining the data, we can see that there are `r vcount(network_igraph)` vertices and `r ecount(network_igraph)` edges in the igraph network. Additional features include:

Feature | T/F?
------- | ----
Bipartite | `r is_bipartite(network_igraph)`
Directed | `r is_directed(network_igraph)`
Weighted | `r is_weighted(network_igraph)`

Comparing the igraph object to the statnet object, we can see that the same network features hold true.
`r print(network_statnet)`

We can now take a dyad census to get an initial understanding of the connections in our network.

```{r}
igraph::dyad.census(network_igraph)
sna::dyad.census(network_statnet)
```

For some reason, the two network objects are returning different measurements with respect to the number of dyad types. This will require further exploration at a later point.

Next, we examine triads using a census

```{r}
igraph::triad_census(network_igraph)
sna::triad.census(network_statnet)
```

Despite the odd results of the dyad census, the triad census does show identical measurements across the two network object types. To double check that all triads are counted, we can calculate the number of potential triads as (550 * 549 * 548)/6 = `r 550 * 549 * 548 / 6`. Then, we sum the number of triads in our census sum(igraph::triad_census(network_igraph)) = `r sum(igraph::triad_census(network_igraph))`. The numbers match so we know our function worked correctly.

Finally, we can look at transitivity within the network to determine the proportion of complete triads in the network. 

```{r}
transitivity(network_igraph)
gtrans(network_statnet)
```

Here, we see that the transitivity calculatuons differ between the two different network objects. This is likely because the statnet function calculates transitivity slightly differently for directed networks and omits certain triads missing information. However, both functions return a relatively high transitivity score, which makes sense given that this network is specifically intended to involve significant leveraging of connections and wheeling-dealing which requires more transitivity.
