---
title: "stm_clusters"
author: "Maddi Hertz"
date: "5/2/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(tidyverse)
library(tidymodels)
library(tidygraph)
library(tidytext)
library(broomExtra)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
library(quanteda.textmodels)
library(janitor)
library(stm)
library(stminsights)
library(kableExtra)
library(ggnetwork)
library(igraph)
library(cowplot)

# read in data
cba_clust_df <- read_csv("cba_clust_df.csv", show_col_types = FALSE)
```

Utilities - to be used later
```{r}
my_stopwords <- c("lhe", "january", "february","march", "april", "june", "july", "august", 
                  "september", "october", "november", "december", "a.m", "p.m", "article", 
                  "section", "cornell", "university", "metadata", "page", "1he", "kentucky", 
                  "connecticut", "york", "philadelphia", "kansas", "putnam", "lancaster", "angeles", 
                  "santa", "california", "pennsylvania", "monroe", "jersey", "barbara", "edward", 
                  "henry", "southwest", "canada", "southern", "alaska", "minnesota", "dakota", 
                  "north", "south", "ohio", "emplo", "shallbe", "fromthe","followingthe", "michigan", 
                  "paragraph", "subjectto", "ence", "wort", "gary", "ions", "10the", "david", 
                  "dennis", "jefferson", "title", "employee_is", "employee_who", "employee_shall", 
                  "employee_has", "employeewill", "purposeof", "returnto", "memorandum", "agreement", 
                  "employee", "employer")

my_tokens <- function(corpus) {
  corpus  %>%
    tokens(remove_symbols = T, remove_punct = T, remove_numbers = T) %>%
    tokens_remove(stopwords("en")) %>%
    tokens_toupper() %>%
    tokens_remove("^M{0,4}(CM|CD|D?C{0,3})(XC|XL|L?X{0,3})(IX|IV|V?I{0,3})$", valuetype = 'regex') %>%
    tokens_remove(min_nchar = 4) %>%
    tokens_remove(max_nchar = 20) %>%
    tokens_remove(my_stopwords) %>%
    tokens_ngrams(n = 1:2)
}

# Metadata: same as cba_clust_df but without the `text` column so it isn't too big
clust_meta <- cba_clust_df %>%
  select(-text)

```

In theory, now that we've identified five union clusters we can use the clusters in the topic model
The three main clusters are industrial, building, and service.
The other two are "health" and "sports". We don't have enough documents to do anything with the sports contracts. And while "health" (includes nurses and hospital based service workers) is pretty similar to "service" its better for it to be its own cluster because if we were to include it, it would ruin our chances of a healthcare coverage topic.

Subset corpus into three corpora and run separate topic models for each cluster (building trades, industrial trades, service sector)
```{r}
# gives you how many documents are in each cluster
tabyl(clust_meta, union_clust_lab)

# corpus with all documents
cba_corpus <- corpus(cba_clust_df)

# tokenize
cba_tokens <- my_tokens(cba_corpus)

# create and trim dfm
cba_dfm <- dfm(cba_tokens)
dim(cba_dfm) #3.3M #3.17M
cba_trim_dfm <- dfm_trim(cba_dfm, min_docfreq = .03, max_docfreq = .9, docfreq_type = "prop") 
dim(cba_trim_dfm) #41K #37K


clust_meta$union_clean <- if_else(is.na(clust_meta$union_clean), "missing", clust_meta$union_clean)

cba_trim_dfm_2 <- dfm_trim(cba_dfm, min_docfreq = .1, max_docfreq = .9, docfreq_type = "prop") %>%
  dfm_remove(pattern = c("employeeshall", "employeesshall", "tlie", "employeeto", "employeeshall", "stan", "corp", "employee_is", "fonh", "1hat", "employmenl"), case_insensitive = TRUE) %>%
  dfm_replace("effective_effective", "effective") %>%
  dfm_replace("provisionsof", "provision") %>%
  dfm_replace("membersof", "member") %>%
  dfm_replace("plan's", "plan") %>%
  dfm_replace("titles", "title") %>%
  dfm_replace("testing", "test") %>%
  dfm_replace("rate_rate", "rate") %>%
  dfm_replace("bargainingunit", "bargaining_unit") %>%
  dfm_replace("requiredto", "required") %>%
  dfm_replace("ovenime", "overtime") %>%
  dfm_replace("vesting", "vest")
# subset corpus
#build_corpus <- corpus_subset(cba_corpus, cba_corpus$union_clust_lab == "building")
#indust_corpus <- corpus_subset(cba_corpus, cba_corpus$union_clust_lab == "industrial")
#service_corpus <- corpus_subset(cba_corpus, cba_corpus$union_clust_lab == "service")

```

Create token object and dfm for each cluster
```{r}
# clean tokens
#build_tokens <- my_tokens(build_corpus)
#indust_tokens <- my_tokens(indust_corpus)
#service_tokens <- my_tokens(service_corpus)

# create dfms
build_dfm <- dfm_subset(cba_trim_dfm, union_clust_lab == "building")
indust_dfm <- dfm_subset(cba_trim_dfm, union_clust_lab == "industrial")
service_dfm <- dfm_subset(cba_trim_dfm, union_clust_lab == "service")

# trim dfms
dim(build_dfm)
build_trim_dfm <- dfm_trim(build_dfm, min_docfreq = .1, max_docfreq = .9, docfreq_type = "prop")
dim(build_trim_dfm) #19K #18K #8K

dim(indust_dfm)
indust_trim_dfm <- dfm_trim(indust_dfm, min_docfreq = .1, max_docfreq = .9, docfreq_type = "prop") %>%
  dfm_remove(pattern = c("employeeshall", "employeesshall", "tlie", "employeeto", "employeeshall", "stan", "corp", "employee_is", "fonh", "1hat", "employmenl"), case_insensitive = TRUE) %>%
  dfm_replace("effective_effective", "effective") %>%
  dfm_replace("provisionsof", "provision") %>%
  dfm_replace("membersof", "member") %>%
  dfm_replace("plan's", "plan") %>%
  dfm_replace("titles", "title") %>%
  dfm_replace("testing", "test") %>%
  dfm_replace("rate_rate", "rate") %>%
  dfm_replace("bargainingunit", "bargaining_unit") %>%
  dfm_replace("requiredto", "required") %>%
  dfm_replace("ovenime", "overtime") %>%
  dfm_replace("vesting", "vest")
dim(indust_trim_dfm) #34K #11K



dim(service_dfm)
service_trim_dfm <- dfm_trim(service_dfm, min_docfreq = .1, max_docfreq = .9, docfreq_type = "prop")
dim(service_trim_dfm) #24K #10K
```

I made it so that the number of terms in each dfm is very similar (range 35K-39K). I assume that will help down the line, when trying to compare them to each other. But maybe it won't, who knows.

Next step: try some topic models
```{r}
clust_meta_build <- clust_meta %>%
  filter(union_clust == 3) %>%
  mutate(year = if_else(is.na(year), 2015, year))



set.seed(02138)
K<-c(5, 8, 10, 16) 
kresult_build <- searchK(build_trim_dfm, K = K, N = floor(.1 * nrow(clust_meta_build)), prevalence = ~ employer + s(year) + union_clean + location + (union_clean * location), content = ~ union_clean, data = clust_meta_build, cores = 3)  


plot(kresult_build)
# let's do 5
######################## need to repeat for each model
######################## try increasing the number of cores


stm_build <- stm(build_trim_dfm, K = 13, prevalence = ~ employer + s(year) + union_clean + location + (union_clean * location), content = ~ union_clean, data = clust_meta_build, init.type = "Spectral", max.em.its = 75, verbose = TRUE, gamma.prior = "L1") 

stm_build_2 <- stm(build_trim_dfm, K = 13, prevalence = ~ employer + s(year) + (union_clean * location), content = ~ union_clean, data = clust_meta_build, init.type = "Spectral", max.em.its = 75, verbose = TRUE, gamma.prior = "L1") 
######################## remove union_clean from prevalence?


sageLabels(stm_build_2)


################# NOT RUN
set.seed(02138)
K<-c(5, 8, 10, 16) 
kresult_indust <- searchK(indust_trim_dfm, 
                          K = K, 
                          N = floor(0.1 * nrow(clust_meta_indust)), 
                          prevalence = ~ employer + union_clean + location, 
                          data = clust_meta_indust, 
                          cores = 3)

###########################################
set.seed(02138)
K<-c(4, 6, 8, 10) 
kresult_indust <- searchK(indust_trim_dfm, K = K, N = floor(0.1 * nrow(clust_meta_indust)), prevalence = ~ employer + union_clean + location, data = clust_meta_indust, cores = 3)
beepr::beep(8)
plot(kresult_indust) 

clust_meta_indust <- clust_meta %>%
  filter(union_clust == 4) %>%
  mutate(location = if_else(location == '-', "NATIONAL", location))

clust_meta_indust$employer

stm_indust <- stm(indust_trim_dfm, 
                  K = 8, 
                  prevalence = ~ employer + union_clean + location, 
                  content = ~ union_clean, 
                  data = clust_meta_indust, 
                  init.type = "Spectral", 
                  max.em.its = 75, 
                  verbose = TRUE, 
                  interactions = FALSE,
                  gamma.prior = "L1")
beepr::beep(8)

sageLabels(stm_indust)

sageLabels(stm_indust_2)


############## trim big, subset, trim small; reweight tf-idf after trim?

stm_topics %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))

```

 
```{r}

stm_indust_effect <- estimateEffect(1:8 ~ employer + union_clean + location, stm_indust, meta = clust_meta_indust, uncertainty = "Global")
summary(stm_indust_effect, topics = 1)

## VISUALIZE: Presenting STM results

# Summary visualization
plot(stm_indust, type = "summary", xlim = c(0, 0.3))

# Metadata/topic relationship visualization
plot(stm_indust, covariate = "rating", topics = c(4, 5, 8), model = stm_indust, method = "difference", cov.value1 = "employer", cov.value2 = "union_clean", xlab = "Management ... Labor", main = "Effect of Management vs. Labor", xlim = c(-0.1, 0.1))


plot(stm_indust, "day", method = "continuous", topics = 3, model = z, printlegend = FALSE, xaxt = "n", xlab = "Time (2008)")
monthseq <- seq(from = as.Date("2008-01-01"), to = as.Date("2008-12-01"), by = "month")
monthnames <- months(monthseq)
axis(1,at = as.numeric(monthseq) - min(as.numeric(monthseq)), labels = monthnames)

# Topical content
plot(stm_indust, type = "perspectives", topics = c(3, 8))

tiff("stm_indust_3_topic_2_wordcloud.tiff", width = 6, height = 6, units = "in", res = 300)
par(bg = "#EEEEEE")
cloud(stm_indust_3, topic = 3, scale = c(2, .25), col = "#003b5c")
dev.off()

mod.out.corr <- topicCorr(stm_indust_3, method = "huge")
plot(mod.out.corr)

ggplot(ggnetwork(mod.out.corr$cor, layout = "geodist"), aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges() +
  geom_nodes(aes(color = "#881c1c", size = 24)) + 
  geom_nodelabel(aes(color = "#881c1c", label = vertex.names),
                 fontface = "bold") +
  theme_blank() +
  theme(panel.background = element_rect(fill = "#EEEEEE"), 
        legend.position = "none")

ggsave("/Users/dananestor/DACSS/Blog/Untitled/docs/stm_indust_3_topic_network.png")


# Semantic Coherence
semantic_indust_3 <- tibble("Topic" = 1:8, "Semantic Coherence" = semanticCoherence(stm_indust_3, indust_trim_dfm, M = 100))
semantic_indust_3 %>%
  ggplot(aes(Topic, `Semantic Coherence`)) +
  geom_col(fill = "#003b5c") +
  theme_cowplot(font_family = "sans") +
  scale_x_continuous(breaks = seq(1, 8, by = 1))
ggsave("/Users/dananestor/DACSS/Blog/Untitled/docs/semantic_indust_3.tiff")

tiff("stm_indust_3_top_topics.tiff", width = 8, height = 6, units = "in", res = 300)
par(bg = "#EEEEEE")
plot(stm_indust_3, type = "summary", col.axis = "#003b5c", fg = "#003b5c", col.main = "#003b5c", col.sub = "#003b5c", xlim = c(0, 1))
dev.off()

# Convergence
plot(stm_indust_3$convergence$bound, type = "l", ylab = "Approximate Objective", main = "Convergence")
```
 

```{r}
# stm_all word cloud
tiff("stm_all_topic_6_wordcloud.tiff", width = 6, height = 6, units = "in", res = 300)
par(bg = "#EEEEEE")
cloud(stm_all, topic = 6, scale = c(2, .25), col = "#63666a")
dev.off()

# stm_all semantic coherence
semantic_all <- tibble("Topic" = 1:8, "Semantic Coherence" = semanticCoherence(stm_all, cba_trim_dfm_2, M = 100))
semantic_all %>%
  ggplot(aes(Topic, `Semantic Coherence`)) +
  geom_col(fill = "#63666a") +
  theme_cowplot(font_family = "sans") +
  scale_x_continuous(breaks = seq(1, 8, by = 1))
ggsave("/Users/dananestor/DACSS/Blog/Untitled/docs/semantic_all.tiff")

tiff("stm_all_top_topics.tiff", width = 8, height = 6, units = "in", res = 300)
par(bg = "#EEEEEE")
plot(stm_all, type = "summary", col.axis = "#63666a", fg = "#63666a", col.main = "#63666a", col.sub = "#63666a", xlim = c(0, 1))
dev.off()

```


